Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-09-04 manuscript/manuscript.tex
Added citation on osprey, discuss linear approach
fixes #148

[ci skip]

@@

>>>>

In the workflow there are multiple hyper parameters to be chosen by the modeler. In our approach we try to optimize a 
parameter at the current stage of the pipeline and continue to the next stage, once a good choice was found. This 
requires the researcher to understand the consequences of non optimal deciscions for the final result. For instance
a non converged clustering could result in lumping states together which should be seperated from each other.

There also exists automatized approaches to optimize all hyper parameters of the pipeline using a cross-validation 
scheme \cite{husic-optimized}. In these approaches the researcher is still required to understand modeling choices like 
sane ranges for parameters to avoid wasting computational time, which is spent to explore meaningless areas of the 
hyperparameter space.
In the sequential approach, one can fall back to the previous step, if one finds a bad result at any following stage. 
This greatly reduces the computational effort and leads to a better understanding of the final model.

%However one will not be able to find a good model based on partially bad modeling choices. E.g. a hidden Markov state 
%model could partially correct bad clusterings, but

@@

\subsection{Modeling large systems}
When estimating MSMs for large systems, challenges may arise that are mostly system dependent.

A case in point is the curse of dimensionality:~it is difficult to discretize a high dimensional feature space. While it is somewhat computationally demanding, more importantly, Euclidean distances become less meaningful with increasing dimensionality~\cite{aggarwal_surprising_2001} and thus cluster assignments based on that norm may yield a poor discretization.
Especially for large systems, it is thus particularly important to first find a suitable set of features, and to further apply dimensionality reduction techniques (e.g.~TICA, VAMP, if applicable) to obtain a low dimensional representation of the slow dynamics.
Hidden Markov models (HMMs) might further mitigate poor discretization to a certain extent~\cite{noe-proj-hid-msm}.

Furthermore, the slowest process in a system as identified by an MSM or HMM might not be the one a modeler is interested in~\cite{banushkina_nonparametric_2015}.
For instance, the slowest process might correspond to a biologically irrelevant side chain flip that only occurred once in the data set.
This problem may be mitigated by choosing a more specific set of features.

Additional technical challenges for large systems include high demands on memory and computation time; we explain how to deal with those in the tutorials.

More details on how to model complex systems with the techniques presented here are described e.g.~by~\cite{plattner_protein_2015,plattner_complete_2017}.
